Extracting Function Signature from R Program Traces

### 2020-05-11 paper/main.tex
Add type grammar

>>>>

\subsection{Type Grammar}
\label{subsec:typegrammar}

\begin{figure}          % Types
    \noindent           % Collapse for readability.
    \centering
    \begin{minipage}{.45\linewidth}
    \begin{flushleft}
    % Types
      $ \begin{array}{lclr}
    D & ::= & {\bf type} \; ID \; T {\bf ;}  & \text{\it type declaration}\\
    T & ::= & {\bf null} & \text{\it unit type} \\
      & |   & {\bf any} & \text{\it top type} \\
      & |   & {\bf environment} & \text{\it environment type} \\
      & |   & {\bf expression} & \text{\it expression type} \\
      & |   & {\bf language} & \text{\it language type} \\
      & |   & {\bf symbol} & \text{\it symbol type} \\
      & |   & {\bf externalptr} & \text{\it externalptr type} \\
      & |   & {\bf pairlist} & \text{\it pairlist type} \\
      & |   & {\bf s4} & \text{\it S4 type} \\
      & |   & {\bf weakref} & \text{\it weakref type} \\
      & |   & S & \text{\it scalar type} \\
      & |   & V & \text{\it vector type} \\
      & |   & \left( T \right) & \text{\it group type} \\
      & |   & T_1 \; {\bf |} \; T_2 & \text{\it union type} \\
      & |   & \langle A_1 , ..., A_n\rangle \Rightarrow T & \text{\it function type} \\
      & |   & {\bf struct}\langle F_1, ..., F_n \rangle & \text{\it struct type} \\
      & |   & {\bf list} \langle T \rangle & \text{\it list type}\\
      & |   & {\bf class}\langle ID_1, ..., ID_n \rangle & \text{\it class type}\vspace{5pt}\\
    \end{array} $
    \end{flushleft}
    \end{minipage}
    \hfill
    \begin{minipage}{.45\linewidth}
    \begin{flushright}
    $ \begin{array}{lclr}
    % Argument Types
    A & ::= & T & \text{\it argument type} \\
      & |   & {\bf ...} \vspace{5pt} \\
    % Field Types
    F & ::= & ID : T & \text{\it struct field}\vspace{5pt}\\
    % Scalar Types
    S & ::= & B & \text{\it scalar types} \\
      & |   & N \vspace{5pt}\\
    % Vector Types
    V & ::= & S \lbrack \rbrack & \text{\it vector types} \vspace{5pt}\\
    % Base Types
    B & ::= & {\bf int} & \text{\it base types} \\
      & |   & {\bf chr} \\
      & |   & {\bf dbl} \\
      & |   & {\bf lgl} \\
      & |   & {\bf clx} \\
      & |   & {\bf raw} \vspace{5pt}\\
    % NA Types
    N & ::= & {\bf \string^int} & \text{\it na types} \\
      & |   & {\bf \string^chr} \\
      & |   & {\bf \string^dbl} \\
      & |   & {\bf \string^lgl} \\
      & |   & {\bf \string^clx} \\
\end{array} $
    \end{flushright}
    \end{minipage}
    \caption{The R type system.}
    \label{fig:types}
\end{figure}
